%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Classicthesis-Styled CV
% LaTeX Template
% Version 1.0 (22/2/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Alessandro Plasmati
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{scrartcl}

\reversemarginpar % Move the margin to the left of the page 

\newcommand{\MarginText}[1]{\marginpar{\raggedleft\itshape\small#1}} % New command defining the margin text style

\usepackage[nochapters]{classicthesis} % Use the classicthesis style for the style of the document
\usepackage[LabelsAligned]{currvita} % Use the currvita style for the layout of the document

\renewcommand{\cvheadingfont}{\LARGE\color{Maroon}} % Font color of your name at the top

\usepackage{hyperref} % Required for adding links and customizing them
\hypersetup{colorlinks, breaklinks, urlcolor=Maroon, linkcolor=Maroon} % Set link colors

\newlength{\datebox}\settowidth{\datebox}{Spring 2011 } % Set the width of the date box in each block

\newcommand{\NewEntry}[3]{\noindent\hangindent=2em\hangafter=0 \parbox{\datebox}{\small \textit{#1}}\hspace{1.5em} #2 #3 % Define a command for each new block - change spacing and font sizes here: #1 is the left margin, #2 is the italic date field and #3 is the position/employer/location field
\vspace{0.5em}} % Add some white space after each new entry

\newcommand{\Description}[1]{\hangindent=2em\hangafter=0\noindent\raggedright\footnotesize{#1}\par\normalsize\vspace{1em}} % Define a command for descriptions of each entry - change spacing and font sizes here

\date{} % Remove the date we get at the end of the CV
%----------------------------------------------------------------------------------------

\begin{document}

\thispagestyle{empty} % Stop the page count at the bottom of the first page

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\begin{cv}{\spacedallcaps{Anhad Jai Singh}}\vspace{1.5em} % Your name

\noindent\spacedlowsmallcaps{Personal Information}\vspace{0.5em} % Personal information heading

\NewEntry{email}{\href{mailto:anhad.jai.singh+resume@gmail.com}{anhad.jai.singh@gmail.com}} % Email address

\NewEntry{website}{\href{https://ffledgling.com}{https://ffledlging.com}} % Personal website

\NewEntry{blog}{\href{https://blog.ffledgling.com}{https://blog.ffledlging.com}} % Blog

\NewEntry{phone}{(M) +91 9989493267} % Phone number(s)

\vspace{1em} % Extra white space between the personal information section and goal

\noindent\spacedlowsmallcaps{About Me}\vspace{1em} % Goal heading, could be used for a quotation or short profile 

\Description{I'm a curious guy, I ask a lot of questions and love to learn. \linebreak
Interested in all things Networking, Linux, Containers, Distributed Systems and Open Source.}
\vspace{1em} % Goal text

%----------------------------------------------------------------------------------------
%	UNDERGRADUATE RESEARCH
%----------------------------------------------------------------------------------------

\noindent\spacedlowsmallcaps{Undergraduate Research}\vspace{1em}

\NewEntry{\mbox{May'13--May'15}}{Honors, \textsc{CVIT}}

\Description{\MarginText{Prof. Anoop M. Namboodiri} Worked to devise classifiers for use in computationally
    restrictive environments such as smartphones. The idea was to make them faster and more
    compact than state-of-the-art classifiers, sacrificing accuracy where necessary. \linebreak
    \begin{itemize}
        \item Proposed a new tree based classifier that was a hybrid of one-vs-one and one-vs-rest classifiers and evaluated and later attempted to optimize its performance along different axes such as speed, memory utilization and accuracy.
        \item In the process of evaluation we came up with a way to visualize the progress and final results of the classifier using d3.js and a small python backend server that would serve the most up-to-date progress status of the classification process.
        \item The full, detailed project report for this project is available at: \href{https://web.iiit.ac.in/~anhadjai.singh/Notes/library}{https://web.iiit.ac.in/~anhadjai.singh/Notes/library}
        \item The visualization for a (static) classifier is available at: \href{https://web.iiit.ac.in/~anhadjai.singh/honors/vis/}{https://web.iiit.ac.in/~anhadjai.singh/honors/vis/}
    \end{itemize}
}

\vspace{1em} % Extra space between major sections

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE
%----------------------------------------------------------------------------------------

\noindent\spacedlowsmallcaps{Work Experience}\vspace{1em}

\NewEntry{\mbox{May'17--Cont.}}{Tech Lead, Cloud Services  --- Gurgaon}

\Description{\MarginText{Tower Research}Working as part of team building on-prem cloud
    infrastructure.
    \linebreak
    \begin{itemize}
        \item Researched, designed, planned, demoed and currently rolling out custom network
            ingress, loadbalancing and DNS solutions for on-perm Kubernetes clusters while working
            with a cross-functional team of experts across timezones.
        \item Evaluated and expanded the capabilities of \href{https://github.com/PowerDNS/pdns}{pdns} and \href{https://github.com/kubernetes-incubator/external-dns/}{external-dns} as part of these efforts, upstreaming changes to benefit the wider community.
    \end{itemize}
    Reference: Neil \textsc{Tiwari}\ \ $\cdotp$\ Team Manager \ $\cdotp$\
    \href{mailto:ntiwari@noreply.com}{\textsc{Request Email}}}
 

% This is a manual page break we toss in because we want logical "sections" to not span across page
% boundaries
\pagebreak
%------------------------------------------------

\NewEntry{\mbox{Aug'15--May'17}}{DevOps, Core Engineering  --- Gurgaon}

\Description{\MarginText{Tower Research}Worked as part of an innately
cross-functional team to improve developer workflow and productivity by writing tooling to automate
and streamline processes.
\begin{itemize}
    \item Designed, proposed and rolled out a revamped, containerized build infrastructure for
        CI/CD using Docker, Kubernetes and Jenkins over 8 months, migrating over 300 jobs used by over 100
        developers in the process.
    \item Worked as part of a team to build, test and roll out the server-side component of a
        meta-SCM system that keeps track of cross-project source dependencies, now widely deployed.
    \item Designed and delivered a simple server-client system used for update notification
        management of command line tools.
\end{itemize}
    Reference: Rahul \textsc{Balani}\ \ $\cdotp$\ Division Manager \ $\cdotp$\
    \href{mailto:rbalani@noreply.com}{\textsc{Request Email}}}

%------------------------------------------------

\NewEntry{\mbox{May'15--Jul'15}}{Release Engineering Intern  --- San Francisco}

\Description{\MarginText{Mozilla}Worked with multiple teams within Mozilla to plan and
execute migrations of legacy services and build configurations and release pipelines to a new
platform based on AWS providing a more robust and reliable setup. Most work involved Ansible,
Docker, AWS and Python. Second project involved working with and migrating workloads to an
internal workload orchestration platform called Taskcluster, built using Docker and
Golang. \\ Reference: Hal \textsc{Wine}\ \
$\cdotp$\ Sr. Release Engineer \ $\cdotp$\ \href{mailto:hwine@noreply.com}{\textsc{Request Email}}}

%------------------------------------------------


\NewEntry{\mbox{Feb'14--Aug'15}}{Junior System Administrator --- Hyderabad}

\Description{\MarginText{IIIT Hyderabad}Worked as Junior System Administrator, managing and
maintaining the Institute's Servers used by over 2000 users.}

%------------------------------------------------

\NewEntry{\mbox{May'14--Aug'14}}{Release Engineering Intern  --- San Francisco}

\Description{\MarginText{Mozilla}Worked with Mozilla's globally distributed team of Release
Engineers to develop a new on-demand partial software update generation system for Firefox called Funsize.\\ Reference: Hal \textsc{Wine}\ \
$\cdotp$\ Sr. Release Engineer \ $\cdotp$\ \href{mailto:hwine@noreply.com}{\textsc{Request Email}}}

%------------------------------------------------

\NewEntry{\mbox{Jun'13-Aug'13}}{Automation \& Tools Intern, Mozilla --- Remote}

\Description{\MarginText{Google Summer of Code}Worked with Mozilla's Automation and Tools Team remotely
to analyze and improve test coverage for an python library suite called Mozbase. \\ Reference: Clint \textsc{Talbert}\
$\cdotp$\ Director Automation \& QA \  $\cdotp$\ \ \href{mailto:cmtalbert@noreply.com}{\textsc{request email}}}

%------------------------------------------------

\vspace{1em} % Extra space between major sections

%----------------------------------------------------------------------------------------
%	TEACHING EXPERIENCE
%----------------------------------------------------------------------------------------

\noindent\spacedlowsmallcaps{Teaching Experience}\vspace{1em}

\NewEntry{\mbox{May'13--May'15}}{Teaching Assistant, \textsc{IT Workshop-I}}

\Description{\MarginText{IIIT-H}Taught the fundamentals of Linux, Shell Scripting and Javascript to
a class of freshmen. Responsibilities included:
    \begin{itemize}
        \item Preparing content for and conducting labs for freshmen.
        \item Creation and evalution of course assignments.
        \item Mid-Term and Final exam evalution.
    \end{itemize}
}

\NewEntry{\mbox{Jul'17--Aug'17}}{Course Instructor, DevTools}

\Description{\MarginText{Tower University}Instructor for an introductory course on version control, build
systems, package managers, details of compilation and linking to campus graduate hires. Responsibilities included:
    \begin{itemize}
        \item Teaching and prepation of course content.
        \item Creation and evalution of course assignments.
    \end{itemize}
}

%------------------------------------------------

% This is a manual page break we toss in because we want logical "sections" to not span across page
% boundaries
\pagebreak

%----------------------------------------------------------------------------------------
%	VOLUNTEER EXPERIENCE
%----------------------------------------------------------------------------------------

\noindent\spacedlowsmallcaps{Volunteer Experience}\vspace{1em}

\NewEntry{\mbox{May'13--May'15}}{Head, \textsc{Open Source Development Group}}

\Description{\MarginText{Open Source Development Group, IIIT-H}Built awareness about F/OSS
software, encouraged contributions to the community. Organized talks and hackathons to
encourage community growth and learning. Greater awareness and encouragement helped increase the
Google Summer of Code selections from 16 (\textsc{GSoC} '12) to 69 (\textsc{GSoC} '14).
\\ Regular writer for the Group's Technical Blog.}

%------------------------------------------------
\NewEntry{\mbox{Jun'14--Nov'14}}{Community Building, \textsc{Release Engineering}}

\Description{\MarginText{Mozilla}Recognized for bringing in and mentoring new contributors. Helped make the team's work more approachable for new volunteers.}

%------------------------------------------------

\NewEntry{\mbox{Dec'12-Dec'13}}{Volunteer Contributor, \textsc{Automation \& Tools}}

\Description{\MarginText{Mozilla}Helped fix numerous bugs across different test suites and testing frameworks.} 

%------------------------------------------------

\vspace{1em} % Extra space between major sections


%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Education}\vspace{0.5em}

\Description{\MarginText{Bachelor's in CS (Hons. CV \& AI)}2011--15\ \ $\cdotp$\ \ International
Institute of Information and Technology, Hyderabad}

%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	ELECTIVES
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Advanced Electives}\vspace{1em}

\Description{\MarginText{Vision \& AI}\textsc{Statistical Methods in AI}, \textsc{Digital Image
Processing}, \textsc{Computer Vision}}
\vspace{-0.5em} % Negative vertical space to counteract the vertical space between every \Description command

\Description{\MarginText{Systems}\textsc{Advanced Computer Networks}, \textsc{Database Systems},
\textsc{Distributed Systems}}
\vspace{-0.5em} % Negative vertical space to counteract the vertical space between every \Description command

\Description{\MarginText{Others}\textsc{Compilers}, \textsc{Principles of Programming Languages}}
\vspace{-0.5em} % Negative vertical space to counteract the vertical space between every \Description command

\Description{\MarginText{Capable}\textsc{C}, \textsc{C++}, \textsc{Go}, \textsc{Javascript}}
\vspace{-0.5em} % Negative vertical space to counteract the vertical space between every \Description command

%----------------------------------------------------------------------------------------
%	SKILLSET
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Skill Set}\vspace{1em}

\Description{\MarginText{Proficient}\textsc{Python}, \textsc{Bash}}
\vspace{-0.5em} % Negative vertical space to counteract the vertical space between every \Description command

\Description{\MarginText{Capable}\textsc{C}, \textsc{C++}, \textsc{Go}, \textsc{Javascript}}
\vspace{-0.5em} % Negative vertical space to counteract the vertical space between every \Description command

\Description{\MarginText{Container Tech}\textsc{Docker}, \textsc{Kubernetes}, \textsc{rkt}}
\vspace{-0.5em} % Negative vertical space to counteract the vertical space between every \Description command

\Description{\MarginText{Ops Miscellany}\textsc{Ansible}, \textsc{helm}, \textsc{Jenkins}, \textsc{Linking and Loading in Linux}}
\vspace{-0.5em} % Negative vertical space to counteract the vertical space between every \Description command

\Description{\MarginText{Compute Clouds}\textsc{Google Compute Engine}, \textsc{AWS}, \textsc{Digital Ocean}}
\vspace{-0.5em} % Negative vertical space to counteract the vertical space between every \Description command

\Description{\MarginText{Operating Systems}Linux(Preferred), OSX, Windows}

\Description{\MarginText{Version Control}\textsc{Git}, \textsc{Mercurial}}
\vspace{-0.5em} % Negative vertical space to counteract the vertical space between every \Description command


%------------------------------------------------

\vspace{1em} % Extra space between major sections

%----------------------------------------------------------------------------------------
%	ONLINE HANDLES
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Online Aliases}\vspace{0.5em}

\Description{\MarginText{}Github\ \ $\cdotp$\ \ \href{https://github.com/ffledgling}{ffledgling}\linebreak
Twitter\ \ $\cdotp$\ \ \href{https://twitter.com/ffledgling}{ffledgling}}

%----------------------------------------------------------------------------------------

\end{cv}

\end{document}
