%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Classicthesis-Styled CV
% LaTeX Template
% Version 1.0 (22/2/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Alessandro Plasmati
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{scrartcl}

\reversemarginpar % Move the margin to the left of the page 

\newcommand{\MarginText}[1]{\marginpar{\raggedleft\itshape\small#1}} % New command defining the margin text style

\usepackage[nochapters]{classicthesis} % Use the classicthesis style for the style of the document
\usepackage[LabelsAligned]{currvita} % Use the currvita style for the layout of the document
\usepackage{fontawesome} % For fancy company logos, Github, LinkedIn, etc.

\renewcommand{\cvheadingfont}{\LARGE\color{Maroon}} % Font color of your name at the top

\usepackage{hyperref} % Required for adding links and customizing them
\hypersetup{colorlinks, breaklinks, urlcolor=Maroon, linkcolor=Maroon} % Set link colors

\newlength{\datebox}\settowidth{\datebox}{Spring 2011 } % Set the width of the date box in each block

\newcommand{\NewEntry}[3]{\noindent\hangindent=2em\hangafter=0 \parbox{\datebox}{\small \textit{#1}}\hspace{1.5em} #2 #3 % Define a command for each new block - change spacing and font sizes here: #1 is the left margin, #2 is the italic date field and #3 is the position/employer/location field
\vspace{0.5em}} % Add some white space after each new entry

\newcommand{\Description}[1]{\hangindent=2em\hangafter=0\noindent\raggedright\footnotesize{#1}\par\normalsize\vspace{1em}} % Define a command for descriptions of each entry - change spacing and font sizes here

\date{} % Remove the date we get at the end of the CV
%----------------------------------------------------------------------------------------

\begin{document}

\thispagestyle{empty} % Stop the page count at the bottom of the first page

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\begin{cv}{\spacedallcaps{Anhad Jai Singh}}\vspace{1.5em} % Your name

\noindent\spacedlowsmallcaps{Personal Information}\vspace{0.5em} % Personal information heading

\NewEntry{email}{\href{mailto:anhad.jai.singh+resume@gmail.com}{anhad.jai.singh@gmail.com}} % Email address

\NewEntry{website}{\href{https://ffledgling.com}{https://ffledlging.com}} % Personal website

\NewEntry{blog}{\href{https://blog.ffledgling.com}{https://blog.ffledlging.com}} % Blog

\NewEntry{phone}{(M) +91 9989493267} % Phone number(s)

\vspace{1em} % Extra white space between the personal information section and goal

\noindent\spacedlowsmallcaps{About Me}\vspace{1em} % Goal heading, could be used for a quotation or short profile 

\Description{I'm a curious guy, I ask questions and I like to learn. \linebreak
    Interested in all things Networking, Linux, Containers, Distributed Systems and Open Source.}
\vspace{1em} % Goal text

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE
%----------------------------------------------------------------------------------------

\noindent\spacedlowsmallcaps{Work Experience}\vspace{1em}

\NewEntry{\mbox{May'17--Apr'18}}{Tech Lead, Cloud Services  --- Gurgaon}

\Description{\MarginText{Tower Research}Worked as part of a division building out and driving adoption
    of on-premise cloud infrastructure. Responsibilities included individual contributions,
    technical advisory for product teams regarding cloud migrations and container technology.
    Also responsible for structured training of new recruits and mentoring junior engineers within
    the team.
    \begin{itemize}
        \item Designed, wrote and deployed various networking components to expose Kubernetes
            services outside the cluster, bringing the on-prem clusters close to parity with cloud
            providers. Work included rolling out custom network ingress, load-balancing and DNS
            solutions. This reduced time to provision a service from a few days to a few seconds,
            removed any single points of failure in the networking stack and added self-recovery
            capabilities. The project required understanding of container networking, iptables, DNS
            and working with golang. As part of these efforts, I also contributed to OSS projects
            such as
            \href{https://github.com/PowerDNS/pdns/pulls?utf8=\%E2\%9C\%93&q=is\%3Apr\%20author\%3Affledgling\%20}{pdns}
            and
            \href{https://github.com/kubernetes-incubator/external-dns/pulls?utf8=\%E2\%9C\%93&q=is\%3Apr\%20author\%3Affledgling\%20}{external-dns}
        \item Helped product teams on-board various applications such as simulations, back-testing, backend
            API servers etc. onto Kubernetes/Cloud Infrastructure, acting as the primary point of
            communication and escalation.
    \end{itemize}
    Reference \#1: Neil \textsc{Tiwari}\ \ $\cdotp$\ Team Manager \ $\cdotp$\
    \href{mailto:ntiwari@noreply.com}{\textsc{Request Email}} \\
    Reference \#2: Myung \textsc{Cho}\ \ $\cdotp$\ CTO \ $\cdotp$\
    \href{mailto:mcho@noreply.com}{\textsc{Request Email}}}
 

%------------------------------------------------

\NewEntry{\mbox{Aug'15--May'17}}{DevOps, Core Engineering  --- Gurgaon}

\Description{\MarginText{Tower Research}Worked as part of an innately
cross-functional team with various responsibilities ranging from build \& release engineering,
writing developer productivity tools, to on-call support and server administration.
\begin{itemize}
    \item Designed and rolled out revamped, containerized build infrastructure for CI/CD using
        Docker, Kubernetes and Jenkins over 8 months, migrating over 300 jobs used by over 100
        developers in the process. Evaluation involved setting up A/B testing and metrics collection
        for the project, which showed a 35\% improvement in speed and a drastic reduction in
        intermittent failures.
    \item Wrote various components in Python for an in-house git based meta-SCM system for
        cross-repo dependencies, including the API server, test harness, and update notification
        system.
    \item Helped migrate the development stack from Fedora20 to Fedora22, including recompiling over
        a hundred in-house and open-source packages and trouble-shooting linking, loading and
        runtime errors in applications.
    \item Responsible for the administration and support of our Gitolite, Gerrit, Jenkins, Jira
        and Apache servers as well as in-house developer productivity tooling.
\end{itemize}
    Reference: Rahul \textsc{Balani}\ \ $\cdotp$\ Division Manager \ $\cdotp$\
    \href{mailto:rbalani@noreply.com}{\textsc{Request Email}}}

\pagebreak
\thispagestyle{empty} % Stop the page count at the bottom of the first page
%------------------------------------------------

\NewEntry{\mbox{May'15--Jul'15}}{Release Engineering Intern  --- San Francisco}

\Description{\MarginText{Mozilla}Worked with multiple teams within Mozilla to plan and execute
migrations of existing services and CI builds to newer, more robust in-house cloud based platforms.
Most work involved Ansible, Docker, AWS and an internal platform called Taskcluster.
\linebreak
Also helped make the team's work more approachable for newcomers and earned recognition for bringing in and mentoring new contributors. \\ Reference:
Hal \textsc{Wine}\ \ $\cdotp$\ Sr. Release Engineer \ $\cdotp$\
\href{mailto:hwine@noreply.com}{\textsc{Request Email}}}

%------------------------------------------------


\NewEntry{\mbox{Feb'14--Aug'15}}{Junior System Administrator --- Hyderabad}

\Description{\MarginText{IIIT Hyderabad}Worked as Junior System Administrator, managing and
maintaining the Institute's desktops and servers used by over 2000 users.}

% This is a manual page break we toss in because we want logical "sections" to not span across page
% boundaries
% \pagebreak
%------------------------------------------------

\NewEntry{\mbox{May'14--Aug'14}}{Release Engineering Intern  --- San Francisco}

\Description{\MarginText{Mozilla}Worked with Mozilla's globally distributed team of Release
Engineers across timezones, to develop a new on-demand software update generation system for Firefox
called Funsize to thereby reduce the time and effort needed to support custom upgrade pathways.
Written in Python and hosted on AWS.\\ Reference: Hal \textsc{Wine}\ \ $\cdotp$\ Sr. Release
Engineer \ $\cdotp$\ \href{mailto:hwine@noreply.com}{\textsc{Request Email}}}

%------------------------------------------------

\NewEntry{\mbox{Jun'13-Aug'13}}{Automation \& Tools Intern, Mozilla --- Remote}

\Description{\MarginText{Google Summer of Code}Worked with Mozilla's Automation and Tools Team
remotely to analyse and improve test coverage for 10+ python libraries (called Mozbase) by over
150\%, while coordinating with each component owner to ensure correct and necessary coverage.\\
Reference: Clint \textsc{Talbert}\ $\cdotp$\ Director Automation \& QA \  $\cdotp$\ \
\href{mailto:cmtalbert@noreply.com}{\textsc{request email}}}

%------------------------------------------------

\vspace{1em} % Extra space between major sections


%----------------------------------------------------------------------------------------
%	VOLUNTEER EXPERIENCE
%----------------------------------------------------------------------------------------

\noindent\spacedlowsmallcaps{Volunteer Experience}\vspace{1em}

\NewEntry{\mbox{May'13--May'15}}{Head, \textsc{Open Source Development Group}}

\Description{\MarginText{Open Source Development Group, IIIT-H}Built awareness about F/OSS
software, encouraged contributions to the community. Organized talks and hackathons to
encourage community growth and learning. Greater awareness and encouragement helped increase the
Google Summer of Code selections from 16 (\textsc{GSoC} '12) to 69 (\textsc{GSoC} '14).
\\ Regular writer for the Group's Technical Blog.}

%------------------------------------------------

% Removed because not very useful
%%% \NewEntry{\mbox{Dec'12-Dec'13}}{Volunteer Contributor, \textsc{Automation \& Tools}}
%%% 
%%% \Description{\MarginText{Mozilla}Helped fix numerous bugs across different test suites and testing frameworks.} 

\vspace{1em} % Extra space between major sections

%----------------------------------------------------------------------------------------
%	SKILLSET
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Skill Set}\vspace{1em}

\Description{\MarginText{Proficient}\textsc{Python}, \textsc{Bash}}
\vspace{-0.5em} % Negative vertical space to counteract the vertical space between every \Description command

\Description{\MarginText{Rudimentary}\textsc{C}, \textsc{C++}, \textsc{Go}, \textsc{Javascript}}
\vspace{-0.5em} % Negative vertical space to counteract the vertical space between every \Description command

\Description{\MarginText{Misc}\textsc{Docker}, \textsc{Kubernetes}, \textsc{Qemu/KVM}, \textsc{Ansible},
\textsc{Jenkins}, \textsc{influxdb}, \textsc{Apache}, \textsc{Git} }
\vspace{-0.5em} % Negative vertical space to counteract the vertical space between every \Description command

\Description{\MarginText{Compute Clouds}\textsc{Google Compute Engine}, \textsc{AWS}, \textsc{Digital Ocean}}
\vspace{-0.5em} % Negative vertical space to counteract the vertical space between every \Description command

\Description{\MarginText{Operating Systems}RHEL Family, Ubuntu, CoreOS}

%------------------------------------------------

\vspace{1em} % Extra space between major sections

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Education}\vspace{0.5em}

\Description{\MarginText{Bachelor's in CS (Hons. CV \& AI)}2011--15\ \ $\cdotp$\ \ International
Institute of Information and Technology, Hyderabad}

%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	ONLINE HANDLES
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Online Presence}\vspace{0.5em}

\Description{\MarginText{``ffledgling''}
\href{https://github.com/ffledgling}{\faGithub} \ \ $\cdotp$\ \
\href{https://twitter.com/ffledgling}{\faTwitter} \ \ $\cdotp$\ \
\href{https://stackoverflow.com/users/1220089/ffledgling}{\faStackOverflow}
}

%----------------------------------------------------------------------------------------

\end{cv}

\end{document}
