%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Classicthesis-Styled CV
% LaTeX Template
% Version 1.0 (22/2/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Alessandro Plasmati
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{scrartcl}

\reversemarginpar % Move the margin to the left of the page 

\newcommand{\MarginText}[1]{\marginpar{\raggedleft\itshape\small#1}} % New command defining the margin text style

\usepackage[nochapters]{classicthesis} % Use the classicthesis style for the style of the document
\usepackage[LabelsAligned]{currvita} % Use the currvita style for the layout of the document

\renewcommand{\cvheadingfont}{\LARGE\color{Maroon}} % Font color of your name at the top

\usepackage{hyperref} % Required for adding links	and customizing them
\hypersetup{colorlinks, breaklinks, urlcolor=Maroon, linkcolor=Maroon} % Set link colors

\newlength{\datebox}\settowidth{\datebox}{Spring 2011 } % Set the width of the date box in each block

\newcommand{\NewEntry}[3]{\noindent\hangindent=2em\hangafter=0 \parbox{\datebox}{\small \textit{#1}}\hspace{1.5em} #2 #3 % Define a command for each new block - change spacing and font sizes here: #1 is the left margin, #2 is the italic date field and #3 is the position/employer/location field
\vspace{0.5em}} % Add some white space after each new entry

\newcommand{\Description}[1]{\hangindent=2em\hangafter=0\noindent\raggedright\footnotesize{#1}\par\normalsize\vspace{1em}} % Define a command for descriptions of each entry - change spacing and font sizes here

\date{} % Remove the date we get at the end of the CV
%----------------------------------------------------------------------------------------

\begin{document}

\thispagestyle{empty} % Stop the page count at the bottom of the first page

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\begin{cv}{\spacedallcaps{Anhad Jai Singh}}\vspace{1.5em} % Your name

\noindent\spacedlowsmallcaps{Personal Information}\vspace{0.5em} % Personal information heading

\NewEntry{email}{\href{mailto:anhad.jai.singh+resume@gmail.com}{anhad.jai.singh@gmail.com}} % Email address

\NewEntry{website}{\href{http://ffledgling.com}{http://ffledlging.com}} % Personal website

\NewEntry{blog}{\href{http://blog.ffledgling.com}{http://blog.ffledlging.com}} % Blog

\NewEntry{phone}{(M) +91 9989493267} % Phone number(s)

\vspace{1em} % Extra white space between the personal information section and goal

\noindent\spacedlowsmallcaps{Aboue Me}\vspace{1em} % Goal heading, could be used for a quotation or short profilEx-n and Full-Time learner. \linebreak

\Description{I'm a Pythonista, Ex-SysAdmin and Full-Time learner. \linebreak
Anything to do with Python, Networks, Systems or Open Source excites me.  
New cutting edge Tools and Technology never fail to fascinate me. \linebreak
Currently working as a DevOps Engineer at Tower Research Capital.}
\vspace{2em} % Goal text

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE
%----------------------------------------------------------------------------------------

\noindent\spacedlowsmallcaps{Work Experience}\vspace{1em}

\NewEntry{Aug '15--Cont.}{DevOps Engineer, Core Engineering  --- Gurgaon}

\Description{\MarginText{Tower Research}Working on improving developer workflow and productivity by
automating and streamlining processes. Currently in charge of building and deploying packages
for the internal package manager. Additionally working with Jenkins, Gerrit and Git.\\ Reference: \textsc{Not Available}}

%------------------------------------------------

\NewEntry{May--Jul '15}{Release Engineering Intern  --- San Francisco}

\Description{\MarginText{Mozilla}Worked with multiple teams within Mozilla to plan and
execute migrations of existing services and build configurations to newer systems/platforms with
more robust setups. Most work involved Ansible, Docker, AWS and an
internal platform called Taskcluster.\\ Reference: Hal \textsc{Wine}\ \
$\cdotp$\ Sr. Release Engineer \ $\cdotp$\ \href{mailto:hwine@mozilla.com}{hwine@mozilla.com}}

%------------------------------------------------


\NewEntry{'14 -- Aug'15}{Junior System Administrator --- Hyderabad}

\Description{\MarginText{IIIT Hyderabad}Worked as Junior System Administrator, managing and
maintaining the Institute's Servers used by over 2000 users.}

%------------------------------------------------

\NewEntry{May-Aug '14}{Release Engineering Intern  --- San Francisco}

\Description{\MarginText{Mozilla}Worked with Mozilla's globally distributed team of Release
Engineers to develop a new software update generation system called Funsize.\\ Reference: Hal \textsc{Wine}\ \
$\cdotp$\ Sr. Release Engineer \ $\cdotp$\ \href{mailto:hwine@mozilla.com}{hwine@mozilla.com}}

%------------------------------------------------

\NewEntry{Jun-Aug '13}{Automation \& Tools Intern, Mozilla --- Remote}

\Description{\MarginText{Google Summer of Code}Worked with Mozilla's Automation and Tools Team remotely
to analyze and improve test coverage for internal python libraries called Mozbase. \\ Reference: Clint \textsc{Talbert}\
$\cdotp$\ Director Automation \& QA \  $\cdotp$\ \ \href{mailto:ctalbert@mozilla.com}{ctalbert@mozilla.com}}

%------------------------------------------------

\vspace{1em} % Extra space between major sections

\pagebreak

%----------------------------------------------------------------------------------------
%	VOLUNTEER EXPERIENCE
%----------------------------------------------------------------------------------------

\noindent\spacedlowsmallcaps{Volunteer Experience}\vspace{1em}

\NewEntry{Jun--Nov '14}{Community Building, \textsc{Release Engineering}}

\Description{\MarginText{Mozilla}Recognized for bringing in and mentoring new contributors. Helped make the team's work more approachable for new volunteers.}

%------------------------------------------------

\NewEntry{Dec '12-'13}{Volunteer Contributor, \textsc{Automation \& Tools}}

\Description{\MarginText{Mozilla}Helped fix numerous bugs across different test suites and testing frameworks.} 

%------------------------------------------------

\NewEntry{May '13--Cont.}{Head, \textsc{Open Source Development Group}}

\Description{\MarginText{Open Source Development Group, IIIT-H}Built awareness about F/OSS
software, encouraged contributions to the community. Organized talks and hackathons to
encourage community growth and learning. Greater awareness and encouragement helped increase the
Google Summer of Code selections from 16 (\textsc{GSoC} '12) to 69 (\textsc{GSoC} '14).
\\ Regular writer for the Group's Technical Blog.}

%------------------------------------------------

\vspace{1em} % Extra space between major sections


%----------------------------------------------------------------------------------------
%	ACADEMIC PROJECTS
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Academic Projects}\vspace{1em}

\NewEntry{Monsoon '13}{Attendance System} 

\Description{\MarginText{Statistical Methods in AI}Developed a prototype of a photograph based
    attendance system. \linebreak
    The prototype showed over 75\% recognition accuracy and involved Facial Recognition utilizing
    PCA, Eigen Vectors, SVM and research from ` Turk \& Pentland: Eigenfaces for Recognition 1991,
MIT Vision and Modelling group. '}
%------------------------------------------------

\NewEntry{Spring '14}{Search Engine}

\Description{\MarginText{Information Retrieval and Extraction}Designed and implemented a prototype search engine in python which utilizes Natural Language processing libraries for keyword extraction and performs indexing based on a Posting list and inverted Indices. Tests on the Wikipedia corpus showed good Relevance with both Human subjects and DCG based methods.}

%------------------------------------------------

\vspace{1em} % Extra space between major sections

%----------------------------------------------------------------------------------------
%	SKILLSET
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Skill Set}\vspace{1em}

\Description{\MarginText{Proficient}\textsc{Python}, \textsc{Bash}}
\vspace{-0.5em} % Negative vertical space to counteract the vertical space between every \Description command

\Description{\MarginText{Basic}\textsc{C}, \textsc{C++}, \textsc{Javascript}}
\vspace{-0.5em} % Negative vertical space to counteract the vertical space between every \Description command

\Description{\MarginText{Version Control}\textsc{Git}, \textsc{Mercurial}}
\vspace{-0.5em} % Negative vertical space to counteract the vertical space between every \Description command

\Description{\MarginText{Misc}\textsc{Docker}, \textsc{Ansible}, \textsc{AWS}, \textsc{Linking and Loading in Linux}}
\vspace{-0.5em} % Negative vertical space to counteract the vertical space between every \Description command

\Description{\MarginText{Operating Systems}Linux(Preferred), OSX, Windows}

%------------------------------------------------

\vspace{1em} % Extra space between major sections

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Education}\vspace{0.5em}

\Description{\MarginText{Bachelor's in CS (Hons. CV \& AI)}2011--2015\ \ $\cdotp$\ \ International Institute of Information and Technology, Hyderabad}

%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	ONLINE HANDLES
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Online Aliases}\vspace{0.5em}

\Description{\MarginText{}Github\ \ $\cdotp$\ \ \href{https://github.com/ffledgling}{ffledgling}\linebreak
Twitter\ \ $\cdotp$\ \ \href{https://twitter.com/ffledgling}{ffledgling}}

%----------------------------------------------------------------------------------------

\end{cv}

\end{document}
